---
title: "HW-2 Classification: Piyaporn Puangprasert"
output: html_notebook
---

## Class: 33:136:487:01 LG SCALE DATA ANALY

##### Prof. Jin Wang

##### Piyaporn Puangprasert(pp712) team with Steven Panagakos (He may sent separate homework)

##### Due date: Mar 3, 2024
##### --------------------------------------------------------------

##### read the Weekly file
```{r}
library(ISLR2)
# load "Weekly" data set
attach(Weekly)
pairs(Weekly)
```

```{r}
names(Weekly)
```

#### Veiw full Weekly data set

```{r}
View(Weekly)
```

## model weeklyview: Direction with 5 lag
```{r}
WeeklyView = glm(Direction~Lag1+Lag2+Lag3+Lag4+Lag5+Volume, data=Weekly, family=binomial)
summary(WeeklyView)
```
#### Answer I. Base on this result, only Lag 2 appears to be statistically significant because of the p-value < 0.05

#### II.Compute the Comfusion matrix and overall fraction of correct predictions
```{r}
predicted_dir <- ifelse(predict(WeeklyView, type = "response") > 0.5, "Up", "Down")
conf_matrix <- table(predicted_dir, Weekly$Direction)
conf_matrix
overall_correct <- sum(diag(conf_matrix)) / sum(conf_matrix)
overall_correct
```
##### The confusion matric can showsthe type of mistakes make by the logistic regression model. It shows ho w correct classify Up or Down. /the identifies type of errors made by model that can be the wrong class. For example this True Positive (TP is up 557), True Negatives(TN )is "Down " 54 times when the market down. False Positive(FT) shows incorrect predicted at 48, and False Negative is Down 430 
 
#### Calculate prediction =(57+557)/(54 + 48 + 430+557) = 0.56

```{r}
(557+54)/(54+48+430+557)
```
#### the Up trends = 557/(48+557) = 0.92
```{r}
557/(557+48)
```
#### the Down trend = 54/(430+54)
```{r}
54/(54+430)
```
 
## 2. Divide the full data set and Training set
```{r}
train_data = Weekly[1:900,]
test_data = Weekly [901:nrow(Weekly),]
```
 
#### 2.2 Fit the logistic regression model using the training data set with Lag2 as only precidtor
```{r}
train_model = glm(Direction~ Lag2, data = train_data, family = binomial)
```

#### 2.3 Comput the confusion matrix and overall fraction of the test data
 
### confusion matrix
```{r}
# glm.all
glm.all = glm(Direction~., data = Weekly, family = "binomial")

# get predict probability
prob = predict(glm.all, newdata = Weekly, type = 'response')


pred = rep('Down', nrow(Weekly))
pred[prob>0.5]= 'Up'

# confusion matrix
table(pred,Weekly$Direction)

```
# from outsource
```{r}
test_prob <- predict(train_model, newdata = test_data, type = "response")
test_predicted_direction <- ifelse(test_prob > 0.5, "Up", "Down")

test_conf_matrix <- table(test_predicted_direction, test_data$Direction)
test_overall_correct <- sum(diag(test_conf_matrix)) / sum(test_conf_matrix)

test_overall_correct
```
### 2.4
```{r}
thresholds <- c(0.52, 0.53, 0.54)
best_correct <- 0
best_threshold <- 0

for (threshold in thresholds) {
  train_preds <- ifelse(predict(train_model, type = "response") > threshold, "Up", "Down")
  train_conf_matrix <- table(train_preds, train_data$Direction)
  train_correct <- sum(diag(train_conf_matrix)) / sum(train_conf_matrix)
  
  if (train_correct > best_correct) {
    best_correct <- train_correct
    best_threshold <- threshold
  }
}

best_threshold
 
```
### That mean the 0.53 threshold gives the best result.

### 2.5
```{r}
test_preds <- ifelse(predict(train_model, newdata = test_data, type = "response") > best_threshold, "Up", "Down")
new_test_conf_matrix <- table(test_preds, test_data$Direction)
new_test_overall_correct <- sum(diag(new_test_conf_matrix)) / sum(new_test_conf_matrix)

new_test_overall_correct
```
### 3.1
```{r}
library(MASS)
lda_model <- lda(Direction ~ Lag2, data = train_data)
```

### 3.2 
```{r}
lda_test_pred <- predict(lda_model, newdata = test_data)$class
lda_test_conf_matrix <- table(lda_test_pred, test_data$Direction)
lda_test_overall_correct <- sum(diag(lda_test_conf_matrix)) / sum(lda_test_conf_matrix)
lda_test_overall_correct
```

## test_overall_correct is 0.5396835 and lda_test_overall_correct is 0.5449735 lad_test have more percentate correction prediction.




















