---
title: "R Notebook"
output: html_notebook
---



```{r}
library(ISLR2)
dat = Hitters
dat = na.omit(dat)
```

```{r}
full.model = lm(Salary~., data = dat)
summary(full.modelw)
                # 
                
```
# Best subsetion
```{r}
library(leaps)
```

```{r}
best.subset = regsubsets(Salary ~., data = dat, nvmax = 19) # fix the one show only 8 => 19
summary(best.subset)
```

# We need to pick the best model
```{r}
reg.summary = summary(best.subset)
reg.summary$which
```


```{r}
reg.summary = summary(best.subset)
reg.summary$outmat # rsq, adjR^@
``````
```{r}
reg.summary = summary(best.subset)
reg.summary$rsq # rsq, adjR^@
```
```{r}
reg.summary = summary(best.subset)
reg.summary$adjr2 # rsq, adjR^@
```

```{r}
i=which.max(reg.summary$adjr2)
i
```
# can count only TRUE
```{r}
reg.summary$which[i,]
```

# what if need do not see the false
```{r}
vars = reg.summary$which[i,]
vars[1]
vars[2]
```
# get the name 
```{r}
vars = reg.summary$which[i,]
names(vars)[vars][-1]
```
```{r}
vars.selected = names(vars)[vars]-1
#best.model = lm(Saraly~vars.selected, data = dat) error

```

```{r}
vars.selected = name(vars)[vars]-1
#dat.seleected = dat[vars.selected]
#v=c('AtBat','Hits')
#dat[v]
vars.selected[8] = 'Lea
```
















