---
title: "HW 1 Piyaporn (pp712) separate work of the group"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

## Class: 33:136:487:01 LG SCALE DATA ANALY

##### Prof. Jin Wang

##### Piyaporn Puangprasert(pp712) This homework we separate work from Steven

##### Due date: Feb 15, 2024
##### --------------------------------------------------------------

##### read the data file

```{r}
dat = read.csv("Auto1a.csv")
names(dat)
```

### 2. mutiple linear regression 

##### Scatterplot matrix that include all the variable in the dataset

```{r}
library(ISLR2)
dat = read.csv("Auto1a.csv")
pairs(Auto)

```
##### Compute the matrix of correlations between the variables using the function

```{r}
cor= cor(dat[,-9])
cor
```

##### Use the lm() function to perform a multiple linear regression with mpg as the response and all other variables except name as the predictors. Use the summary() function to print the results. Comment on the output.

##### Is there a relationship between the predictors and the response? 
###### Answer: Yes, b/c the  relationship between the predictors and the response of weight, year, and origin ( p-value < 0.05)

##### Which predictors appear to have a statistically significant relationship to the response? 
###### Answer: Yes, b/c the  relationship between the predictors and the response of weight, year, and origin ( p-value < 0.05)

##### What does the coefficient for the year variable suggest? 

###### Answer:  the coefficient for the year variable suggest is 0.730911899


```{r}
model4 = lm(mpg~. - name, data = dat)
summary(model4)
``` 
##### Use the * symbols to fit linear regression models with interaction effects. Do any interactions appear to be statistically significant?
##### Answer Yes,it shows the p-value < 0.05

```{r}
model5 = lm(mpg ~ horsepower * weight ,data = dat)

summary(model5)
```

## model_interaction
```{r}
model_interaction = lm(mpg ~.*.-name, data=dat)

summary(model_interaction)
```

## model-3: coefficients

```{r}
model4$coefficients
```
## mpg and year
```{r}
model = lm(mpg~year, data = dat)
summary(model)
```
#### Answer the mpg and year are both have siatistically significant relationship to the response variable b/c the p value < 0.05

