---
title: "HW 1 "
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

## Class: 33:136:487:01 LG SCALE DATA ANALY

##### Prof. Jin Wang

##### Piyaporn Puangprasert(pp712) This homework we separate work 

##### Due date: Feb 15, 2024
##### --------------------------------------------------------------

##### read the data file

```{r}
dat = read.csv("Auto1a.csv")
names(dat)
```

## model-1: mpg~horsepower
```{r}
model = lm(mpg~horsepower, data = dat)
```

**coefficients**
```{r}
model$coefficients
```
**CI**
```{r}
confint.lm(model)
```
**summary**
```{r}
summary(model)
```
##### a hypothesis test 
##### hypothesis,
##### H0 : β1 = β2 = ··· = βp = 0
##### versus the alternative
##### Ha : at least one βj is non-zero

##### hypothesis test is performed by computing the F-statistic
##### This F-statistic = 535.8 on 1 that means  it  evidence against the null hypothesis H0. Or the large F-statistic suggests that at least one of the advertising media must be related to mpg.

##### I.Is there a relationship between the predictor and the response? Why?
##### Answer: Yes, b/c the coefficient for the predictor(horspower) is significantly differnt from zero. The "p-value" at B0 and B1 < 2.2e-16" < 0.05 (very small) or there is an association between the predictor and the response. 

##### II. How strong is the relationship between the predictor and the response?

##### Answer: After checking at R square = 0.6 (not strong relationship between the mpg and hourspower(predictor and the response)) ( if close to 1 that means strong relationship)

##### III. Is the relationship between the predictor and the response positive or negative? 
##### Answer: Yes, b/c p value less than 0.05 (response negative)

##### IV What is the Predicted mpg with hoursepower of 98%
##### Answer: a housepower is giving 23.86675 of mpg or the predicted mpg for a horsepower of 98 is approximately 23.87.

```{r}

predict_mpg = predict(model, data.frame(horsepower = 98))
predict_mpg
```

















