---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

# Simple LR
## Read dataset

```{r}
dat = read.csv("Advertising.csv")

```

## model-1: Sales~TV
```{r}
model = lm(Sales~TV, data = dat)
```

**coefficients**
```{r}
model$coefficients
```
**CI**
```{r}
confint.lm(model)
```
**summary**
```{r}
summary(model)
```

```{r}
model$fitted.values
model$residuals

hist(model$residuals)
```
## plot
```{r}
b = model$coefficients[1]
a = model$coefficients[2]

plot(dat$TV, dat$Sales, pch=20) # plot(dat$Sales ~ dat$TV)
# abline(b,a, col='red',lwd=2)
abline(model$coefficients, col='red',lwd=2)
```

## model-2: Sales~radio
```{r}
model2 = lm(Sales~Radio, data = dat)
summary(model2)
```

## model-3: Sales~Newspaper
```{r}
model3 = lm(Sales~Newspaper, data = dat)
summary(model3)
```
# multiple LR
## model 4
```{r}

# model4 = lm(Sales~TV+Radio+Newspaper, data=dat)
model4 = lm(Sales~., data=dat)

summary(model4)
```
## correlation
```{r}
cor(dat)
```


```{r}
plot(dat$Radio, dat$Newspaper, pch=20)
```

## adj-R^2
```{r}
m1 = lm(Sales~TV, data=dat)
summary(m1)
```

## why R-sq is not good
add one more variable with random values

```{r}
set.seed(0201)
x = sample(1:200)
x2 = sample(1:200)
x3 = sample(1:200)


m2 = lm(Sales~TV+x+x2+x3, data = dat)
summary(m2)
```
## prediction, CI, PI
```{r}

model4 = lm(Sales~., data=dat)

summary(model4)

```

### prediction
```{r}
new_data = data.frame(
  TV = c(200, 250),
  Radio = c(100, 50),
  Newspaper = c(20, 50)
)
  
predict(model4, newdata = new_data)
```
### CI
```{r}
predict(model4, newdata = new_data, interval = 'confidence')
```
### PI
```{r}
predict(model4, newdata = new_data, interval = 'predict')
```

# Qualitative preditors

```{r}
library(ISLR2)

model_own = lm(Balance~Own, data = Credit)

summary(model_own)

```
```{r}
model_region = lm(Balance~Region, data = Credit)
summary(model_region)
```

## relevel
```{r}
Region_a = relevel(Credit$Region, ref="South")

model_region_a = lm(Balance~Region_a, data = Credit)
summary(model_region_a)
```
# Interaction
```{r}
# model_interaction = lm(Sales ~ TV*Radio, data=dat)
model_interaction = lm(Sales ~ TV+Radio+TV:Radio, data=dat)

summary(model_interaction)
```
# Qudratic model
```{r}
model_q = lm(mpg~horsepower+I(horsepower^2), data=Auto)
summary(model_q)
```

# scatterplot matrix
```{r}
library(ISLR2)

pairs(Auto)
# plot(Auto)

```

```{r}
model = lm(mpg~displacement+weight, data = Auto)

model.1 = lm(mpg~displacement+weight + displacement*weight, data = Auto) 

summary(model)
summary(model.1)
```
# other considerations
## 1. nonlinearity
```{r}
library(ISLR2)
model = lm(mpg~.-name, data=Auto)
summary(model)
```
Residual plot
```{r}
plot(model$residuals~model$fitted.values)
```
```{r}
model.2 = lm(sqrt(mpg)~.-name, data=Auto)
plot(model.2$residuals~model.2$fitted.values)
```

```{r}
model.log = lm(log(mpg)~.-name, data=Auto)
plot(model.log$residuals~model.log$fitted.values)
```
## 4. outlier
```{r}
boxplot(Auto$horsepower)
```

## 6. collinearity
```{r}
pairs(Auto)
```
```{r}
model.displacement = lm(displacement~.-mpg-name, data=Auto)

smry = summary(model.displacement)
smry$r.squared
```

```{r}
vif.displacement = 1/(1-smry$r.squared)
vif.displacement
```







